Supplementary Material for: A Rough Guide to Pre-processing High-Frequency Animal Tracking Data

### 2021-02-04 _02_filtering_data.Rmd
return to outside panel title

```{r add_outlier, eval=FALSE}
# make a copy
data_copy <- copy(data)

# add a prolonged spike or reflection to 300 positions
data_copy[500:800, `:=`(
  x = x + 0.25,
  y = y + 0.25
)]

# add normal error
data_copy[, `:=`(
  x = do_add_error(x, std_dev = 0.01),
  y = do_add_error(y, std_dev = 0.005)
)]

# add 100 outliers
data_copy <- do_add_outliers(data_copy, p_data = 0.005, std_dev = 0.1)
```

@@

```{r eval=FALSE}
fwrite(data_copy, file = "data/data_errors.csv")
```

@@

```{r echo=FALSE}
# plot data inside and outside bbox
fig_filter_bounds <-
  ggplot() +
  geom_point(
    data = data_inside_bbox,
    aes(x, y),
    col = pal[3],
    alpha = 1, size = 0.2
  ) +
  geom_point(
    data = data_copy[!data_inside_bbox,
      on = c("x", "y")
    ],
    aes(x, y),
    col = "grey",
    shape = 4,
    size = 0.2
  ) +
  geom_path(
    data = data,
    aes(x, y),
    col = "grey20",
    alpha = 1
  ) +
  geom_hline(
    yintercept = c(0.5, 1),
    col = "grey",
    lty = 2
  ) +
  ggthemes::theme_few() +
  theme(
    axis.text = element_blank(),
    axis.title = element_blank(),
    plot.title = element_text(
      face = "bold",
      margin = margin(t = 30, b = -30),
      hjust = 0.1
    )
  ) +
  theme(plot.background = element_rect(fill = NA)) +
  coord_equal(expand = T) +
  labs(
    title = "(a)"
  )
```

@@

```{r echo=FALSE}
# data plot
fig_outlier_remove <-
  ggplot() +
  geom_path(
    data = data_copy,
    aes(x, y),
    col = "grey",
    lwd = 0.2
  ) +
  geom_point(
    data = data_copy[500:800, ],
    aes(x, y),
    # size = 0.5,
    alpha = 0.6,
    shape = 4, col = pal[5]
  ) +
  geom_point(
    data = data_copy[!data_copy[500:800, ],
      on = c("x", "y")
    ],
    aes(x, y,
      col = (in_speed >= 0.03 & out_speed >= 0.03),
      shape = (in_speed >= 0.03 & out_speed >= 0.03),
      size = (in_speed >= 0.03 & out_speed >= 0.03)
    ),
    show.legend = F,
    alpha = 1
  ) +
  geom_path(
    data = data,
    aes(x, y),
    col = "grey20",
    alpha = 1
  ) +
  scale_color_manual(values = c(pal[3], pal[1])) +
  scale_shape_manual(values = c(1, 4)) +
  scale_size_manual(
    values = c(0.2, 2)
  ) +
  ggthemes::theme_few() +
  theme(
    axis.text = element_blank(),
    axis.title = element_blank(),
    plot.title = element_text(
      face = "bold",
      margin = margin(t = 30, b = -30),
      hjust = 0.1
    )
  ) +
  coord_equal() +
  theme(plot.background = element_rect(fill = NA)) +
  labs(
    title = "(b)"
  )
```

@@

```{r echo=FALSE}
# wrap plot
figure_01 <-
  wrap_plots(
    fig_filter_bounds,
    fig_outlier_remove
  )

>>>>

```{r add_outlier, eval=FALSE}
# make a copy
# data_copy <- copy(data)
# 
# # add a prolonged spike or reflection to 300 positions
# data_copy[500:800, `:=`(
#   x = x + 0.25,
#   y = y + 0.25
# )]
# 
# # add normal error
# data_copy[, `:=`(
#   x = do_add_error(x, std_dev = 0.01),
#   y = do_add_error(y, std_dev = 0.005)
# )]
# 
# # add 100 outliers
# data_copy <- do_add_outliers(data_copy, p_data = 0.005, std_dev = 0.1)
```

@@

```{r eval=FALSE}
# fwrite(data_copy, file = "data/data_errors.csv")
```

@@

```{r echo=FALSE}
# plot data inside and outside bbox
fig_filter_bounds <-
  ggplot() +
  geom_point(
    data = data_inside_bbox,
    aes(x, y),
    col = pal[3],
    alpha = 1, size = 0.2
  ) +
  geom_point(
    data = data_copy[!data_inside_bbox,
      on = c("x", "y")
    ],
    aes(x, y),
    col = "grey",
    shape = 4,
    size = 0.2
  ) +
  geom_path(
    data = data,
    aes(x, y),
    col = "grey20",
    alpha = 1
  ) +
  geom_hline(
    yintercept = c(0.5, 1),
    col = "grey",
    lty = 2
  ) +
  ggthemes::theme_few() +
  theme(
    axis.text = element_blank(),
    axis.title = element_blank()
  ) +
  theme(plot.background = element_rect(fill = NA)) +
  coord_equal(expand = T)
```

@@

```{r echo=FALSE}
# data plot
fig_outlier_remove <-
  ggplot() +
  geom_path(
    data = data_copy,
    aes(x, y),
    col = "grey",
    lwd = 0.2
  ) +
  geom_point(
    data = data_copy[500:800, ],
    aes(x, y),
    # size = 0.5,
    alpha = 0.6,
    shape = 4, col = "black"
  ) +
  geom_point(
    data = data_copy[!data_copy[500:800, ],
      on = c("x", "y")
    ],
    aes(x, y,
      col = (in_speed >= 0.03 & out_speed >= 0.03),
      shape = (in_speed >= 0.03 & out_speed >= 0.03),
      size = (in_speed >= 0.03 & out_speed >= 0.03)
    ),
    show.legend = F,
    alpha = 1
  ) +
  geom_path(
    data = data,
    aes(x, y),
    col = "grey20",
    alpha = 1
  ) +
  scale_color_manual(values = c(pal[3], "grey")) +
  scale_shape_manual(values = c(1, 4)) +
  scale_size_manual(
    values = c(0.2, 2)
  ) +
  ggthemes::theme_few() +
  theme(
    axis.text = element_blank(),
    axis.title = element_blank()
  ) +
  coord_equal() +
  theme(plot.background = element_rect(fill = NA))
```

@@

```{r echo=FALSE}
# wrap plot
figure_01 <-
  wrap_plots(
    fig_filter_bounds,
    fig_outlier_remove
  )+
    plot_annotation(
      tag_levels = "a",
      tag_prefix = "(",
      tag_suffix = ")"
    ) &
  theme(plot.tag = element_text(face = "bold"))
